Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams

### 2014-12-22 Paper/paper.tex
Data section and some future work.

Dropping terms not dependent on counts, we can calculate the probability 
required for Gibbs sampling as follows:

@@

Where $\tilde c (d_i, f)$ is the number of VSO's in document $d_i$ assigned to frame $f$,
$\tilde c(d_i)$ is the number of VSO's in document $i$,
$\tilde c(f,w_{ij}^a)$ is the number of VSOs containing $w_{ij}^a$ as argument $a$ that are
assigned to frame $f$, and
$\tilde c(f)$ is the number of VSOs assigned to frame $f$.
Note that $\tilde c$ indicates a count that does not consider the contribution of 
VSO $w_{i,j}$.

We will see that the data used in this probject doesn't contain any document-level
information. As a result, we adapt model 1 by grouping VSOs with the same verb into ``documents''.
This move leverages the dirichlet prior $\alpha$ to enforce sparcity of frames 
accross verbs, but of course cannot capture the information given by the kind of
document-level semantic sparsity seen in LDA.\footnote{When we use verbs as
documents (i.e, $D = V^v$), since $w_{ij}^v$ is the same for all verbs in document $d_i$ 
(and $d_i$ is the only document with that verb), it follows that the number of VSO's in document 
$d_i$ belonging to frame $f$ is the same as the number of VSO's with $w_{ij}^v$ as their verb assigned to 
frame $f$; that is, $\tilde c(d_i, f) = \tilde c(f, w_{ij}^v)$.}

\section{Data}

\subsection{Google Syntactic-ngrams}
Here we talk a bit about the syntactic n-grams and all that \citep{ngrams2013}.
\begin{itemize}
    \item A syntactic-ngram is a $k$-word rooted subtree for some sentence. 
    \item Google ngrams come from a corpus of 3.5 million English books.
    \item We trimmed the ``verb args'' dataset to consider only subject-verb-object triples (VSO's).
    \item The dataset contains 1,629,120 unique VSO's with a total of 96,245,401 by count.
    \item In our final results we may only use the most common \%20 of these...
\end{itemize}

\subsection{Pruning}

@@

\section{Future Work}
\begin{itemize}
\item Come up with models that are specifically for independent tuples.
\item Use more of the arguments in verbargs.
\item Use year information -- do frames change over time?
\item Consider subjet/object pairs instead of independent.
\end{itemize}

>>>>

Dropping terms not dependent on counts, we can calculate the proportional
probability required for Gibbs sampling as follows:

@@

Where $\tilde c (d_i, f)$ is the number of VSO's in document $d_i$ assigned to frame $f$;
$\tilde c(d_i)$ is the number of VSO's in document $i$;
$\tilde c(f,w_{ij}^a)$ is the number of VSOs containing $w_{ij}^a$ as argument $a$ that are
assigned to frame $f$; and
$\tilde c(f)$ is the number of VSOs assigned to frame $f$.
Note that $\tilde c$ indicates a count that does not consider the contribution of 
$w_{i,j}$.

The data used in this probject (see section \ref{data}) doesn't contain any document-level
information. As a result, we adapt model 1 by grouping VSOs with the same verb into ``documents''.
This move leverages the dirichlet prior $\alpha$ to enforce sparcity of frames 
accross verbs, but of course cannot capture the information given by the kind of
document-level semantic sparsity seen in LDA.\footnote{When we use verbs as
documents (i.e, $D = V^v$), since $w_{ij}^v$ is the same for all verbs in document $d_i$ 
(and $d_i$ is the only document with that verb), it follows that the number of VSO's in document 
$d_i$ belonging to frame $f$ is the same as the number of VSO's with $w_{ij}^v$ as their verb assigned to 
frame $f$; that is, $\tilde c(d_i, f) = \tilde c(f, w_{ij}^v)$.}

\section{Dataset - Verbargs}
\label{data}

Verbargs is the subset of Google's syntactic-ngram corpus for training our 
models and evaluating the reults 
A syntactic-ngram is a $k$-word rooted subtree of some sentence.
The ngrams in Google's corpus were extracted from 3.5 million books and are labled with
Penn Treebank part-of-speech tags Stanford-basic dependency lables \citep{ngrams2013}.
Each ngram also includes frequency counts by year.
In this project, used the

The ngrams in the verbargs dataset (130M items) consist of a verb and all of its 
immediate arguments.
From this dataset, we consider only VSO's, that is; we pruned verbargs to only
those ngrams containing a subject (nsubj) and object (dobj) whose immediate parent
is the ngram's root verb (1.6M items, 96M by count). 
We further trimmed the data to consider only the \%25 most common verbs 
(800K items, 78M by count).

@@

\section{Future Work}
One big weakness of this project over the results of \citet{oconnor2013} is that 
we could not used document-level context to leverage semantic information.
A possible direction of future reseach is to create models that take better 
advantage of the syntax-level context provided by syntactic ngrams. 
One easy way to do this would be to modify model 1 so that the argument 
vocabulary ranges over subject/object pairs instead of individual nouns.
or object.
More advanced models would take better advantage of the various kinds of arguments
in verbargs and their relation to one another.
For example, you might be gleen some semantic information about the relationship between
verbs and prepositional objects by the preposition that mediates them: 
That you ''swim \emph{in} the lake'' versus ``ice skate \emph{on} the lake'' 
indicates that the relationship between swimming and lakes is different from the one between
ice skating and lakes.
